```{r}
library(tidyverse)
```
 1. Read in `districts.csv` into a tibble named `districts`. How many rows and columns does it contain?
```{r}
districts <- read_csv('data/districts.csv')
```
```{r}
print(nrow(districts))
print(ncol(districts))
```
```{r}
str(districts)
```
```{r}
dim(districts)
```


2. Notice that the first row corresponds to the whole State of Tennessee. Remove this row and save the result back to `districts'

```{r}
districts <- districts %>%
    filter(system_name != 'State of Tennessee')
```

```{r}
districts <-districts[-c(1), ]

```
```{r}
districts
`

``
3. How many districts have a proficiency rate of at least 80% for both alg_1 and eng_1?
```{r}
districts %>% 
  select(system, system_name, alg_1, eng_1) %>% 
  filter(alg_1 >= 80.0 & eng_1 >= 80.0)
```
```{r}
#filter(alg_1 >= 80, eng_1 >=80)
```
```{r}
#sum(districts$alg_1 >= 80 & districts$eng_1 >= 80, na.rm = T)

#sum(districts$alg_1 >= 80 & districts$eng_1 >= 80, na.rm = T)
```

```{r}
districts %>% 
  filter(alg_1 >= 80.0 & eng_1 >= 80.0) %>%
  count()
```
. How many districts have a proviciency rate less than 50% for either alg_1 or eng_1?
```{r}
districts %>% 
  select(system, system_name,alg_1, eng_1) %>% 
  filter(alg_1 <= 50.0 | eng_1 <= 50.0) 
```
```{r}
districts %>% 
  select(system, system_name,alg_1, eng_1) %>% 
  filter(alg_1 <= 50.0 | eng_1 <= 50.0) %>%
  count()
```
5. Which district has the lowest graduation rate?
```{r}
districts %>% 
  summarise(min(grad, na.rm = TRUE))
```
```{r}
districts %>% 
  #select(system_name, grad, region)%>%
  slice_min(grad)
```
```{r}
districts %>% 
  slice_min(grad)
```
```{r}
LowestGraduation <- districts %>% 
  filter(grad == min(grad, na.rm=TRUE)) %>% 
   transmute(system_name, grad)
LowestGraduation
```
```{r}
districts%>%
  filter(grad == min(grad, na.rm=TRUE))
```
```{r}
districts %>%
  arrange(grad) %>% 
  head(1)
```

6. Within the Mid Cumberland region, which district has the highest ACT composite?

```{r}
districts %>%
  select(system_name, act_composite, region)%>%
  filter (region == "Mid Cumberland") %>% 
  slice_max(act_composite)
  
```
```{r}
MidCumACT <- districts %>% 
  filter(region == "Mid Cumberland") %>% 
  filter(act_composite == max(act_composite, na.rm=TRUE)) %>% 
  transmute(system_name, act_composite)
MidCumACT
```

7. Create a histogram showing the distribution of graduation rates. What can you say about this distribution?

```{r}
districts %>%
drop_na(grad) %>%
ggplot(aes(x = grad)) +
geom_histogram(binwidth = 5, color="black", fill="blue") +
scale_x_continuous(name = "Graduation rates in %", breaks=c(20, 40, 60, 70, 80, 90, 100))+
scale_y_continuous(name = "Count") +
ggtitle("Distribution of Graduation rates")
```
```{r}
districts %>%
drop_na(grad) %>%
ggplot(aes(x = grad)) +
geom_histogram(binwidth = 5, color="black", fill="blue") +
labs(x= "Graduation rates in %", y = 'Count')+
ggtitle("Distribution of Graduation rates")
```
```{r}
districts_grad <- districts %>%
  select(grad)

ggplot(districts, aes(grad,  fill = region)) +
  geom_histogram(bins = 20, alpha = 20, na.rm =TRUE) +
  facet_wrap(~ region)
```
```{r}

```

8. Create a scatter plot to compare alg_1 proficiency rates to alg_2 rates. What do you notice? Facet this plot by region. Does anything stand out when you facet the plots?

```{r}
districts %>%
ggplot(aes(x = alg_1, y=alg_2, color = region)) +
geom_point(na.rm = TRUE) +
facet_wrap("region")
```
```{r}

districts %>% 
  ggplot(aes(x=alg_1, y=alg_2)) +
  facet_wrap(vars(region)) +
  geom_point(na.rm=TRUE) +
  xlim(0,100) +
  ylim(0,100)
```

9. Create a bar chart showing the total enrollment by region. Which region has the highest total enrollment? Which has the smallest?
```{r}
library(scales)
```

```{r}
districts %>%
  select (enrollment, region) %>% 
  group_by(region) %>%
  drop_na(enrollment) %>%
  summarize(total_enrollement = sum(enrollment)) %>%
  ggplot(aes(x = region, y = total_enrollement)) +
  geom_col()
 
```
```{r}
districts %>% 
  ggplot(aes(enrollment, region, fill = region)) +
  geom_bar(stat='identity', na.rm = TRUE) + 
  geom_col(position = 'dodge') +
  labs(y = 'Total Enrollment', x = 'Region',   
  title = 'Total Enrollment By Region') +
  scale_x_continuous(labels = comma)
```
```{r}
ggplot(districts, aes(x=region,y=enrollment, fill=region))+
  geom_col()+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  scale_y_continuous(name = 'Enrollment in 100k', labels = unit_format(scale = 1e-5, unit = ''))
```

10. When creating this bar chart you may have noticed that some districts have missing enrollment values. For how many districts is this the case?


```{r}
districts %>% 
  filter(is.na(enrollment)) %>% 
  transmute(system_name)
```

```{r}
sum(is.na(districts$enrollment))
```


```{r}
nrow(districts %>%
  group_by(region) %>%
  summarize(na_enrollment=sum(is.na(enrollment))) 

```

11. What is the mean graduation rate across all districts? What might be wrong with using just the regular mean to assess average graduation rates?

```{r}
districts %>%
  drop_na(grad) %>%
  summarize(Average_Graduation_Rate = mean(grad))
```

```{r}
summary(districts$grad)
```

```{r}
summarise(districts, meanGrad = mean(grad, , na.rm = TRUE))
```


12. Redo the previous question but use a weighted average (`weighted.mean`) graduation across all districts, weighing by enrollment. How much does this change your answer? Can you explain using the data the reason for the big change from using the mean?

```{r}
districts %>%
  drop_na(enrollment) %>% 
  summarize(Average_Graduation_Rate = weighted.mean(grad, enrollment, na.rm = TRUE))

```


```{r}
weighted.mean(districts$grad, dplyr::coalesce(districts$enrollment,0), na.rm=TRUE)
```


13. Create a boxplot showing graduation rates per region. Does anything stand out?
```{r}
districts %>%
  group_by(region) %>%
  ggplot(aes(x = region, y = grad)) +
  geom_boxplot(na.rm = TRUE)
```

```{r}
districts %>%
arrange(grad, region) %>%
ggplot(aes(grad, region, fill = region)) +
geom_boxplot(na.rm = TRUE) +
xlim(0,100)
```

```{r}
districts %>% 
  ggplot(aes(x=grad, y=region)) +
  geom_boxplot(na.rm=TRUE) +
  scale_x_continuous(breaks=seq(0,100,10))
```




14. Find the weighted average of graduation rates by region using enrollment as weights. Compare the results you get for the weighted average to what you see from the boxplots.

```{r}
districts %>%
  group_by(region) %>% 
  drop_na(enrollment) %>% 
  summarize(Weighted_Average = weighted.mean(grad, enrollment, na.rm = TRUE))

```

```{r}
districts %>% 
  drop_na(grad, enrollment) %>% 
  group_by(region) %>% 
  summarize(w_mean = weighted.mean(grad, enrollment),
            sd = sd(grad))
```



15. For many districts, values for `alg_2` are lower than for `alg_1`. Create a histogram showing the distribution of differences (`alg_1` - `alg_2`). Which school had the largest drop from `alg_1` to `alg_2`? For what percentage of schools is it true that `alg_2` is larger than `alg_1`? Is there a similar drop off for `eng_2` and `eng_3`?

```{r}
districts %>% 
  mutate(system_name, alg_1, alg_2, Difference = alg_1 - alg_2) %>%
  ggplot(aes(x = Difference)) +
  geom_histogram(binwidth = 5, color="black", fill="blue", na.rm = TRUE)
```
```{r}
districts %>% 
  mutate(system_name, alg_1, alg_2, Difference = alg_1 - alg_2) %>%
   slice_max(Difference)
```
```{r}
districts %>% 
    filter(alg_2 > alg_1) %>% 
    count()
   
```
```{r}
districts %>% 
  mutate(system_name, eng_2, eng_3, difference = eng_2 - eng_3) %>%
  ggplot(aes(x = difference)) +
  geom_histogram(binwidth = 5, color="black", fill="blue", na.rm = TRUE)
```

```{r}
districts %>% 
  mutate (system_name, eng_2, eng_3, difference = eng_2 - eng_3) %>%
   slice_max(difference)
```
```{r}
districts %>% 
    filter(eng_3 > eng_2) %>% 
    count()
```

16. You may have noticed that a lot of rows are missing values. Which district has the largest number of missing values? What do you notice about schools that have a lot of missing values?
```{r}
library(dplyr)
count_na_func <- function(x) sum(is.na(x)) 

districts %>%
  mutate(count_na = apply(., 1, count_na_func))
```
 
 
17. Find the correlation between graduation rate and all other variables. Create a horizontal bar chart showing these correlations. Make sure that your plot is ordered by correlation values. What do you notice from these correlations?
```{r}
districts_noNA <- na.omit(districts) %>%
select(where(is.numeric))
data_cor <- cor(districts_noNA[ , colnames(districts_noNA) != "grad"],  districts_noNA$grad)
data_cor
```

 
18. Create a scatterplot for `grad` vs. `suspended`. Does what you see make sense given your answer from the previous part?

```{r}
districts %>%
ggplot(aes(x = grad, y=suspended)) +
geom_point(na.rm = TRUE) 
```

19. Create a linear regression model using `lm` with target variable `grad` and predictor variable `suspended`. What R^2 value does this model have? What is the interpretation of this number?
```{r}
simple_regression_model <- lm(grad ~ suspended,
                              data =districts)
summary(simple_regression_model)
```

20. Add the regression line to your scatterplot using `geom_smooth` with `method='lm'`. How do you feel about the regression line after seeing it plotted on the scatterplot?

```{r}
districts %>%
ggplot(aes(x = grad, y=suspended)) +
geom_point(na.rm = TRUE) + 
geom_smooth(method="lm", col="black")
```

21. Read in the school-level testing data for 2014, available [here](https://www.tn.gov/content/dam/tn/education/data/data_2014_school_base.xlsx). You might find the readxl library useful for this task. If you use this library, be sure to look at the `na` argument for the `read_excel` function.

```{r}
library(readxl)
```

```{r}
School_2014 <- read_excel('data/data_2014_school_base.xlsx', na = c("*", "**"))
```

22. How many schools have at least 20 percent of students below bsc for Algebra I? Which districts do these schools belong to?
```{r}
School_2014 %>% 
  filter(subject == 'Algebra I' &  pct_below_bsc <= 20) %>%
  count()
```
```{r}
School_2014 %>% 
  filter(subject == 'Algebra I' &  pct_below_bsc <= 20) 
```

