```{r}
library(tidyverse)
```
 1. Read in `districts.csv` into a tibble named `districts`. How many rows and columns does it contain?
```{r}
districts <- read_csv('data/districts.csv')
```
2. Notice that the first row corresponds to the whole State of Tennessee. Remove this row and save the result back to `districts'
```{r}
districts <-districts[-c(1), ]

```
```{r}
districts
```
3. How many districts have a proficiency rate of at least 80% for both alg_1 and eng_1?
```{r}
districts %>% 
  select(system, system_name, alg_1, eng_1) %>% 
  filter(alg_1 >= 80.0 & eng_1 >= 80.0)
```
```{r}
districts %>% 
  filter(alg_1 >= 80.0 & eng_1 >= 80.0) %>%
  count()
```
. How many districts have a proviciency rate less than 50% for either alg_1 or eng_1?
```{r}
districts %>% 
  select(system, system_name,alg_1, eng_1) %>% 
  filter(alg_1 <= 50.0 | eng_1 <= 50.0) 
```
```{r}
districts %>% 
  select(system, system_name,alg_1, eng_1) %>% 
  filter(alg_1 <= 50.0 | eng_1 <= 50.0) %>%
  count()
```
5. Which district has the lowest graduation rate?
```{r}
districts %>% 
  summarise(min(grad, na.rm = TRUE))
```
```{r}
districts %>% 
  select(system_name, grad, region)%>%
  slice_min(grad)
```

6. Within the Mid Cumberland region, which district has the highest ACT composite?

```{r}
districts %>%
  select(system_name, act_composite, region)%>%
  filter (region == "Mid Cumberland") %>% 
  slice_max(act_composite)
  
```
7. Create a histogram showing the distribution of graduation rates. What can you say about this distribution?

```{r}
districts %>%
drop_na(grad) %>%
ggplot(aes(x = grad)) +
geom_histogram(binwidth = 5, color="black", fill="blue") +
scale_x_continuous(name = "Graduation rates in %")+
scale_y_continuous(name = "Count") +
ggtitle("Distribution of Graduation rates")
```
8. Create a scatter plot to compare alg_1 proficiency rates to alg_2 rates. What do you notice? Facet this plot by region. Does anything stand out when you facet the plots?

```{r}
districts %>%
ggplot(aes(x = alg_1, y=alg_2)) +
geom_point() +
facet_wrap("region")
```
9. Create a bar chart showing the total enrollment by region. Which region has the highest total enrollment? Which has the smallest?
```{r}
districts %>%
group_by(region) %>%
ggplot(aes(x = alg_1, y=alg_2)) +
geom_point() +
facet_wrap("region")
```

